---
output:
  pdf_document: default
  html_document: default
---

```{r, echo = FALSE, message = FALSE,warning=F, include=FALSE}
source("../scripts/setup.R")
```


```{r, echo=FALSE, include=FALSE}
options(knitr.table.format = "latex")
```

# Overview of the data set used. 

## Web-scraping 

The data we are using within this project is coming from the website "Big Bang Theory Transcripts". It is accessible in the following link : 
[https://bigbangtrans.wordpress.com/](https://bigbangtrans.wordpress.com/series-1-episode-1-pilot-episode/)

We decided to web-scrap the data and to create csv files to stock them. Indeed, it is easier for us to get the data and have it locally on our files so that whenever we want to work with them again, we do not need to web-scrap again. We will directly be able to use the files we created. 

```{r include=FALSE}
## DO NOT UN-COMMENT THE CODE UNLESS THERE ARE ANY WEBSCRAPING MODIFICATION TO DO

# # Webscrap the html pages ending to create a loop 
# 
# link.html <- read_html("https://bigbangtrans.wordpress.com/")
# 
# ## Create a list containing all my link endings
# link_end <- link.html %>%
#   html_nodes("#pages-2 a") %>% 
#   html_text2()
# 
# ## convert to lowercase 
# link_end <- tolower(link_end)
# 
# ## remove dash followed by space 
# link_end <- gsub("– ", "", link_end)
# 
# ## replace space by dash
# link_end <- gsub(" ", "-", link_end)
# 
# ## replace 
# link_end <- gsub("series-01-episode-01", "series-1-episode-1", link_end)
# link_end <- gsub("series-01-episode-02", "series-1-episode-2", link_end)
# link_end <- gsub("series-01-episode-03", "series-1-episode-3", link_end)
# link_end <- gsub("series-01-episode-04", "series-1-episode-4", link_end)
# link_end <- gsub("series-01-episode-05", "series-1-episode-5", link_end)
# link_end <- gsub("series-01-episode-06", "series-1-episode-6", link_end)
# link_end <- gsub("series-01-episode-07", "series-1-episode-7", link_end)
# link_end <- gsub("series-01-episode-08", "series-1-episode-8", link_end)
# link_end <- gsub("series-01-episode-09", "series-1-episode-9", link_end)
# link_end <- gsub("series-01", "series-1", link_end)
# link_end <- gsub("series-02", "series-2", link_end)
# link_end <- gsub("series-2-episode-05", "series-2-episode-5", link_end)
# link_end <- gsub("series-2-episode-08", "series-1-episode-08", link_end)
# link_end <- gsub("series-2-episode-10", "series-2-episode-11", link_end)
# link_end <- gsub("series-03", "series-3", link_end)
# link_end <- gsub("series-04", "series-4", link_end)
# link_end <- gsub("series-05", "series-5", link_end)
# link_end <- gsub("series-06", "series-6", link_end)
# link_end <- gsub("series-6-episode-14-the-cooper/kripke-inversion",
#                  "series-6-episode-14-the-cooperkripke-inversion", link_end)
# link_end <- gsub("series-6-episode-23", "series-06-episode-23", link_end)
# link_end <- gsub("series-6-episode-24", "series-06-episode-24", link_end)
# link_end <- gsub("series-07", "series-7", link_end)
# link_end <- gsub("series-08", "series-8", link_end)
# link_end <- gsub("series-8-episode-05", "series-7-episode-05", link_end)
# link_end <- gsub("series-09", "series-9", link_end)

```



```{r include=FALSE}
## DO NOT UN-COMMENT THE CODE UNLESS THERE ARE ANY WEBSCRAPING MODIFICATION TO DO

# ## Loop through my the links with link endings to get the script 
 
# scripts <- data.frame()
# character_speech_1 <- data.frame()
# character_speech_2 <- data.frame()
# character_speech_3 <- data.frame()
# character_speech_4 <- data.frame()
# character_speech_5 <- data.frame()
# character_speech_6 <- data.frame()
# character_speech_7 <- data.frame()
# character_speech_8 <- data.frame()
# character_speech_9 <- data.frame()
# character_speech_10 <- data.frame()
# 
# for(element in 2:length(link_end)){
#   document_id <- paste0("doc", element-2)
#   episode_id <- gsub("-", "_", link_end[element])
#   Link = paste0("https://bigbangtrans.wordpress.com/", link_end[element])
# 
#   if (element < 17){
#     pages = read_html(Link)
#     page_scripts <- pages %>%
#       html_nodes("#post-3 p , .MsoNormal span , .title") %>%
#       html_text2()
# 
#     # element > 40 & element < 113
#    }else if (element == 46){
#    pages = read_html(Link)
#    page_scripts <- pages %>%
#      html_nodes("content p , em , .title") %>%
#      html_text2()
# 
# 
#    }else if (element > 40 & element < 113 ||element == 122){
#    pages = read_html(Link)
#    page_scripts <- pages %>%
#      html_nodes("#content p , .title") %>%
#      html_text2()
# 
#    #132-134 || 132 < element < 152
#    }else if (element == 123 || element > 132 & element < 152 || element > 152 & element < 233){
#    pages = read_html(Link)
#    page_scripts <- pages %>%
#      html_nodes("p+ p , i , .title") %>%
#      html_text2()
# 
#    }
#    else{
#    pages = read_html(Link)
#    page_scripts <- pages %>%
#      html_nodes(".title , #post-68 p , em") %>%
#      html_text2()
#    }
# 
#    page_scripts <- unique(page_scripts)
# 
#    if (element < 19){
#      season <- rep(1, times = length(page_scripts))
#      data_frame_col_characters <- cbind(season, page_scripts)
#      character_speech_1 <- rbind(character_speech_1, data_frame_col_characters)
# 
#   }else if (element > 18 & element < 42 ){
#     season <- rep(2, times = length(page_scripts))
#     data_frame_col_characters <- cbind(season, page_scripts)
#     character_speech_2 <- rbind(character_speech_2, data_frame_col_characters)
# 
#   }else if (element > 41 & element < 65){
#     season <- rep(3, times = length(page_scripts))
#     data_frame_col_characters <- cbind(season, page_scripts)
#     character_speech_3 <- rbind(character_speech_3, data_frame_col_characters)
# 
#   }else if ( element > 64 & element < 89){
#     season <- rep(4, times = length(page_scripts))
#     data_frame_col_characters <- cbind(season, page_scripts)
#     character_speech_4 <- rbind(character_speech_4, data_frame_col_characters)
# 
#   }else if (element > 88 & element < 113){
#     season <- rep(5, times = length(page_scripts))
#     data_frame_col_characters <- cbind(season, page_scripts)
#     character_speech_5 <- rbind(character_speech_5, data_frame_col_characters)
# 
#   }else if (element > 112 & element < 137){
#     season <- rep(6, times = length(page_scripts))
#     data_frame_col_characters <- cbind(season, page_scripts)
#     character_speech_6 <- rbind(character_speech_6, data_frame_col_characters)
# 
#   }else if (element > 136 & element < 161){
#     season <- rep(7, times = length(page_scripts))
#     data_frame_col_characters <- cbind(season, page_scripts)
#     character_speech_7 <- rbind(character_speech_7, data_frame_col_characters)
# 
#   }else if (element > 160 & element < 185){
#     season <- rep(8, times = length(page_scripts))
#     data_frame_col_characters <- cbind(season, page_scripts)
#     character_speech_8 <- rbind(character_speech_8, data_frame_col_characters)
# 
#   }else if (element > 184 & element < 209){
#     season <- rep(9, times = length(page_scripts))
#     data_frame_col_characters <- cbind(season, page_scripts)
#     character_speech_9 <- rbind(character_speech_9, data_frame_col_characters)
# 
#   }else{
#     season <- rep(10, times = length(page_scripts))
#     data_frame_col_characters <- cbind(season, page_scripts)
#     character_speech_10 <- rbind(character_speech_10, data_frame_col_characters)
# 
#   }
#    
#    page_scripts <- paste(page_scripts, collapse='// ')
# 
#    data_frame_col <- c(document_id, episode_id , page_scripts)
#    scripts <- rbind(scripts, data_frame_col)
# 
#    print(episode_id)
# 
# }
# 
# colnames(scripts) <- c("document", "title", "script")
# write.csv(scripts, "../data/series_scripts.csv", row.names = FALSE)
# colnames(character_speech_1) <- c("season", "main_character_script")
# write.csv(character_speech_1, "../data/character_speech_1.csv", row.names = FALSE)
# colnames(character_speech_2) <- c("season", "main_character_script")
# write.csv(character_speech_2, "../data/character_speech_2.csv", row.names = FALSE)
# colnames(character_speech_3) <- c("season", "main_character_script")
# write.csv(character_speech_3, "../data/character_speech_3.csv", row.names = FALSE)
# colnames(character_speech_4) <- c("season", "main_character_script")
# write.csv(character_speech_4, "../data/character_speech_4.csv", row.names = FALSE)
# colnames(character_speech_5) <- c("season", "main_character_script")
# write.csv(character_speech_5, "../data/character_speech_5.csv", row.names = FALSE)
# colnames(character_speech_6) <- c("season", "main_character_script")
# write.csv(character_speech_6, "../data/character_speech_6.csv", row.names = FALSE)
# colnames(character_speech_7) <- c("season", "main_character_script")
# write.csv(character_speech_7, "../data/character_speech_7.csv", row.names = FALSE)
# colnames(character_speech_8) <- c("season", "main_character_script")
# write.csv(character_speech_8, "../data/character_speech_8.csv", row.names = FALSE)
# colnames(character_speech_9) <- c("season", "main_character_script")
# write.csv(character_speech_9, "../data/character_speech_9.csv", row.names = FALSE)
# colnames(character_speech_10) <- c("season", "main_character_script")
# write.csv(character_speech_10, "../data/character_speech_10.csv", row.names = FALSE)

```


## Description of the data sets we created.  

We crated many different files as we want to make several analysis. 

### "series_scripts.csv"
The first csv file is called "series_scripts.csv". It is available in the "data" folder of our project. This data set contains 231 rows and 3 columns:

- Each row represent the script of one episode. In this series of 10 seasons, there is a total of 231 episodes. 
- The column *document* : represent the index and tells us which document it is. The information are in character class. 
- The column *title* : contains the title of the script. It tells us the series and episode number. The information are in character class. 
- The column *script* : contains the whole script for each corresponding episode. Note that we decided to use the symbol '$\\$' for the end-line. This indeed is helpful so that we manage to put the whole script in one cell. The information are in character class. 


```{r echo=FALSE, include=FALSE}
data_scripts <- read.csv("../data/series_scripts.csv")

summary(data_scripts)%>%
  kbl(caption = "Characteristics of the data's columns ")%>%
  kable_styling(latex_options = "HOLD_position")
```


We do not show how the data look like in here, simply because the *scripts* column contains a lot of text and if would take way too much place in the report. You are invited to open the csv files if you want to get an overview. 

```{r chunck_annexe1, echo=FALSE, include=FALSE}
data_scripts[1:1, ] %>%
  kbl(caption = "The 1 first row of the data set *data scripts.csv* ") %>%
  kable_classic(full_width = T, html_font = "Cambria", font_size = 7) %>%
  kable_styling(latex_options = "HOLD_position")
```


### "season_scripts.csv"

We created a second csv file named "season_scripts.csv". Indeed, we quickly realized that the analysis per episode would fast become tedious and less meaningful. Therefore, we decided to aggregate the episodes by season. This way we get all the scripts of each season's episode on one concatenated string.

This data set contains 10 rows, each row representing one season and 2 columns: 

- The column *season* : indicate the season number.
- The column *agg_script* : contains all the aggregated scripts per season. It means that there is the script of each episode of one season within one cell of the dataframe. 

```{r echo=FALSE, include=FALSE}
### Analysis by season and not by episode, should we make an average ?)
# Add a row indicating the season number
data_scripts$season <- c(
  1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,
  2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,
  3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,
  4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,
  5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,5,
  6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,6,
  7,7,7,7,7,7,7,7,7,7,7,7,7,7,7,7,7,7,7,7,7,7,7,7,
  8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,
  9,9,9,9,9,9,9,9,9,9,9,9,9,9,9,9,9,9,9,9,9,9,9,9,
  10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10)
```

```{r echo=FALSE, include=FALSE}
season_scripts <- aggregate(data_scripts$script, list(data_scripts$season),
                            paste, collapse="")
names(season_scripts) <- c("season", "agg_script")
```

```{r echo=FALSE, include=FALSE}
write.csv(season_scripts, "../data/season_scripts.csv", row.names = FALSE)
```


Since the table is quite long and even one row is very long to output, we did not add an annex of the data frame output. We will recommend you to directly go on the csv file if an overview of the data set is needed.

```{r echo=FALSE, include=FALSE}
season_scripts[1:1, ] %>%
  kbl(caption = "The 1 first row of the data set *season scripts.csv* ") %>%
  kable_classic(full_width = T, html_font = "Cambria", font_size = 7) %>%
  kable_styling(latex_options = "HOLD_position")
```



### The various files 'character_speech'
We created 10 other files based on the web-scraping. Indeed, we decided to have one file per season because we wanted to have one row new row each time a character is speaking. 

It means that each file has a different length depending on how many time there is a change of interlocutor. However, each file has the following column structured: 

- One column *season* : indicate the season number the script line is referring to. 
- One column *main_character_script* : is the whole script line with the name of the person speaking 
- One column *character_name* : contains the name of the person speaking the line 
- One column *character_scripts* : contains the script line of the interlocutor

Then we combined all these rows to have one main file named 'character_speech.csv'. The two first rows are printed below so you can have an overview of this dataset.


```{r echo=TRUE,include=FALSE}
## re-import the data
character_speech_1 <- read.csv("../data/character_speech_1.csv")
character_speech_2 <- read.csv("../data/character_speech_2.csv")
character_speech_3 <- read.csv("../data/character_speech_3.csv")
character_speech_4 <- read.csv("../data/character_speech_4.csv")
character_speech_5 <- read.csv("../data/character_speech_5.csv")
character_speech_6 <- read.csv("../data/character_speech_6.csv")
character_speech_7 <- read.csv("../data/character_speech_7.csv")
character_speech_8 <- read.csv("../data/character_speech_8.csv")
character_speech_9 <- read.csv("../data/character_speech_9.csv")
character_speech_10 <- read.csv("../data/character_speech_10.csv")

## define the main characters 
main_characters <- c("Sheldon", "Leonard", "Penny", "Howard", "Raj")

## split the character name and its scripts for each data
character_speech_1[c('character_name',
                     'character_scripts')] <- str_split_fixed(character_speech_1$main_character_script,
                                                              ':', 2)
character_speech_1 <- character_speech_1[character_speech_1$character_name %in% main_characters, ]


character_speech_2[c('character_name',
                     'character_scripts')] <- str_split_fixed(character_speech_2$main_character_script,
                                                              ':', 2)
character_speech_2 <- character_speech_2[character_speech_2$character_name %in% main_characters, ]


character_speech_3[c('character_name',
                     'character_scripts')] <- str_split_fixed(character_speech_3$main_character_script,
                                                              ':', 2)
character_speech_3 <- character_speech_3[character_speech_3$character_name %in% main_characters, ]


character_speech_4[c('character_name',
                     'character_scripts')] <- str_split_fixed(character_speech_4$main_character_script,
                                                              ':', 2)
character_speech_4 <- character_speech_4[character_speech_4$character_name %in% main_characters, ]


character_speech_5[c('character_name',
                     'character_scripts')] <- str_split_fixed(character_speech_5$main_character_script,
                                                              ':', 2)
character_speech_5 <- character_speech_5[character_speech_5$character_name %in% main_characters, ]


character_speech_6[c('character_name',
                     'character_scripts')] <- str_split_fixed(character_speech_6$main_character_script,
                                                              ':', 2)
character_speech_6 <- character_speech_6[character_speech_6$character_name %in% main_characters, ]


character_speech_7[c('character_name',
                     'character_scripts')] <- str_split_fixed(character_speech_7$main_character_script,
                                                              ':', 2)
character_speech_7 <- character_speech_7[character_speech_7$character_name %in% main_characters, ]


character_speech_8[c('character_name',
                     'character_scripts')] <- str_split_fixed(character_speech_8$main_character_script,
                                                              ':', 2)
character_speech_8 <- character_speech_8[character_speech_8$character_name %in% main_characters, ]


character_speech_9[c('character_name',
                     'character_scripts')] <- str_split_fixed(character_speech_9$main_character_script,
                                                              ':', 2)
character_speech_9 <- character_speech_9[character_speech_9$character_name %in% main_characters, ]


character_speech_10[c('character_name',
                     'character_scripts')] <- str_split_fixed(character_speech_10$main_character_script,
                                                              ':', 2)
character_speech_10 <- character_speech_10[character_speech_10$character_name %in% main_characters, ]


## combine all these datasets into one dataset 

character_speech <- rbind(character_speech_1, character_speech_2, character_speech_3,
                          character_speech_4, character_speech_5, character_speech_6, 
                          character_speech_7, character_speech_8, character_speech_9,
                          character_speech_10)


write.csv(character_speech , "../data/character_speech.csv", row.names = FALSE)

```


```{r chunck_annexe2, echo=FALSE}
character_speech[1:2, ] %>%
  kbl(caption = "The 2 first row of the data set *character speech.csv* ") %>%
  kable_classic(full_width = T, html_font = "Cambria", font_size = 7) %>%
  kable_styling(latex_options = "HOLD_position")
```




