---
output:
  html_document: default
  pdf_document: default
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
source("../scripts/setup.R")
```
# Part 3.2 : Sentiment Analysis by character
After the analysis of the script according to the seasons, we wanted to see how the five main characters (Sheldon, Leonard, Penny, Raj and Howard) of the show impact the script of the show through a sentiment analysis. 

We use a data set with which an observation is given for a character according to the sentence he says.  Thus, we can use again here the 'nrc' lexicon and have an idea of the dispersions of the feelings for each of our characters.
# (Should we do the graph with the agg_tbl ?)

```{r}
char.tb <- as_tibble(data.frame(character_speech))

char.tk <- unnest_tokens(
  char.tb,
  output = "word",
  input = "character_scripts",
  to_lower = TRUE,
  strip_punct = TRUE,
  strip_numeric = TRUE)
 
char.tk <- char.tk %>%
  anti_join(stop_words, by = c("word" = "word"))
  
char.sent <- 
  inner_join(
    char.tk,
    get_sentiments("nrc"),
    by = c("word" = "word"))

#head(char.sent, 10) %>% 
  #flextable() %>%
  #autofit()
```

```{r}
char.sent %>% 
  group_by(character_name, sentiment) %>% 
  summarize(n = n()) %>%
  ungroup() %>% 
  ggplot(aes(x = sentiment,
             y = n,
             fill = sentiment)) + 
  geom_bar(stat = "identity",
           alpha = 0.8) + 
  facet_wrap(~character_name) + 
  coord_flip()
```
First, we see in this graph that Sheldon seems to be the most 'intense' character. In the sense that he is the one who uses the most words that can be categorized by a feeling. Then we notice an identical pattern in all the characters. Indeed, we have a prevalence of positive words then negative and on the contrary less words related to the feelings 'trust' and 'disgust'.

Since in the previous analysis negative and positive feelings predominate, we wanted to try to use another dictionary. This is a General purpose English sentiment lexicon that categorizes words in a binary fashion, either positive or negative.

## Negative-Positive Ratio in all seasons by using bing lexicon
```{r echo=FALSE, include=FALSE}
head(get_sentiments(lexicon = "bing"))
```

```{r}
char.sent2 <-
  inner_join(
    char.tk, 
    get_sentiments("bing"),
    by = c("word" = "word"))

char.sent2 %>% 
  group_by(character_name) %>% 
  group_by(season, character_name) %>% 
  count(sentiment) %>%
  ungroup() %>%
  ggplot(aes(season, n, fill = sentiment)) +
  geom_col(position = "fill") +
  geom_text(aes(label = n), position = position_fill(0.5), color = "white")+
  coord_flip()+
  facet_wrap(character_name~.)+
  theme_dark()+
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold")
    )+
  scale_fill_manual(values = c("#EA181E", "chartreuse3"))+
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10))+
  labs(y = NULL,  x = "Season", fill = NULL, title = "Negative-Positive Ratio in all seasons by using bing lexicon")
```
We obtain a surprising result considering our previous findings. Indeed, we notice that the 'negative' represents a major part in all the characters. This is contradictory with the results of the nrc lexicon (why ?). 
We also notice that Sheldon is the most negative character and Penny the most 'positive' character. This analysis is consistent with our previous results.
Also, we can imagine that some seasons are more or less pleasant for our characters. For example, Raj seems to have used more 'positive' words in season 9 and Leonard in season 2 while Sheldon uses more negative than positive words in seasons 1, 3 and 7.

# Valence shifter approach on each character 
```{r echo=FALSE, include=FALSE}
character.speech.text <- get_sentences(agg_tbl)
character.speech.senti <- sentiment(character.speech.text) 
```

```{r echo=FALSE}
character.speech.senti %>% group_by(character_name) %>% 
  ggplot(aes(x = sentence_id, y = sentiment)) + 
  geom_line() +  
  facet_wrap(~ character_name, scale="free_x")

```
The analysis is possible by going through each sentence. The most 'instense' character is Sheldon, he appears to be very expressive in the positive like in the negative. However we can guess that he tends to be less and less negative through the end of the show. The lowest peaks are a little bit less frequent. 

```{r echo=FALSE, include=FALSE}
sentiment_by(character.speech.senti)
```

```{r echo=FALSE}
docnames(char.cp) <- c('Howard', 'Leonard', 'Penny', 'Raj', 'Sheldon')

sentiment_by(character.speech.senti) %>% 
  mutate(characters_names = docnames(char.cp)) %>%
  ggplot(aes(x = reorder(characters_names, ave_sentiment),
             y = ave_sentiment)) + 
  ylab("Avg sentiment") +
  geom_bar(stat = "identity") + 
  coord_flip() + 
  xlab("") 
```
With this barplot, we can once again identify the average sentiment and see that the most positive character is Penny with an average of 0.13, followed by Leonard. The least positive character is Sheldon.
