---
output:
  html_document: default
  pdf_document: default
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
source("../scripts/setup.R")
```

# Part 3.3 : Topic modelling 

## Similarities between season scripts
In this part, we want to compare the similarities of the scripts between the season. We decided to use the 3 similarities measure to compute the similarity matrix: Jaccard similarity, Cosine distance, and Euclidean distance. The best/explanatory method in our case seems to be the Euclidean one and we will therefore concentrate on it for the following.

```{r echo=FALSE}
#season.jac <- textstat_simil(
  #season.tfidf_lemma,
  #method = "jaccard",
  #margin = "documents")

#season.cos <- textstat_simil(
  #season.tfidf_lemma,
  #method = "cosine",
  #margin = "documents")

season.euc <- textstat_dist(
  season.tfidf_lemma,
  method = "euclidean",
  margin = "documents")
```

```{r echo=FALSE}
## Jaccard 
#season.jac.mat <- melt(as.matrix(season.jac)) # Convert the object to matrix then to data frame 
#ggplot(data = season.jac.mat, 
       #mapping = aes(x = Var1, y = Var2, fill = value)) +
  #scale_fill_gradient2(
    #low = "blue",
    #high = "red",
    #mid = "white", 
    #midpoint = 0.5,
    #limit = c(0, 1),
    #name = "Jaccard") +
  #geom_tile() + xlab("") + ylab("")

## Cosine
#season.cos.mat <- melt(as.matrix(season.cos))
#ggplot(
  #data = season.cos.mat,
  #mapping = aes(x = Var1, y = Var2, fill = value)) +
  #scale_fill_gradient2(
    #low = "blue",
    #high = "red",
    #mid = "white",
    #midpoint = 0.5,
    #limit = c(0, 1),
    #name = "Cosine") +
  #geom_tile() + xlab("") + ylab("")

## Euclidean
season.euc.mat <- melt(as.matrix(season.euc))
M <- max(season.euc.mat$value) # maximum distance
season.euc.mat$value.std <- (M - season.euc.mat$value)/M 
# conversion from distance to similarity in [0,1]
ggplot(
  data = season.euc.mat,
  mapping = aes(x = Var1, 
                y = Var2,
                fill = value.std)) +
  scale_fill_gradient2(
    low = "blue",
    high = "red",
    mid = "white", 
    midpoint = 0.5,
    limit = c(0, 1),
    name = "Euclidean") +
  geom_tile() + xlab("") + ylab("")
```
From the Euclidean co-occurence matrix plot, it seems that season 4 is very far away to every other seasons. On the contrary, season 6 and season 2 are quite distant (but we know that there may be a problem in webscrapping).

## Clustering 
Then, to create a cluster, we decide to focus on the Euclidean distance only.

```{r echo=FALSE}
season.hc <- hclust(as.dist(season.euc))
## crude.hc <- hclust(as.dist(1 - crude.jac)) # use this line for Jaccard
## crude.hc <- hclust(as.dist(1 - crude.cos)) # use this line for Cosine
plot(season.hc)

season.clust <- cutree(season.hc, k = 3)
season.clust

season.km <- kmeans(season.tfidf_lemma, centers = 3)
season.km$cluster


data.frame(
  Clust.1 = names(sort(apply(season.tfidf[season.clust==1, ], 2, sum), decreasing = TRUE)[1:5]),
  Clust.2 = names(sort(apply(season.tfidf[season.clust==2, ], 2, sum), decreasing = TRUE)[1:5]),
  Clust.3 = names(sort(apply(season.tfidf[season.clust==3, ], 2, sum), decreasing = TRUE)[1:5])
)
```
Not surprisingly here, we find the same characteristics for seasons 4, 2 and 6 as before regarding their proximities.

## Similarities between words
We use the cosine distance measure to determine the similarities between words. 
#(Euclidean doesn't work and jaccard is very similar so idk which one to take ? + Not useful)
```{r echo=FALSE, include=FALSE}
# Cosine
season.feat <- textstat_frequency(season.dfm_lemma) %>%
  filter(rank <= 50) 
season.feat$feature

season.cos <- textstat_simil(
  season.dfm_lemma[, season.feat$feature],
  method = "cosine",
  margin = "feature")

season.cos.mat <- melt(as.matrix(season.cos)) # Convert the object to matrix then to data frame 

ggplot(data = season.cos.mat, aes(x=Var1, y=Var2, fill=value)) +
  scale_fill_gradient2(
    low = "blue",
    high = "red",
    mid = "white",
    midpoint = 0.5,
    limit = c(0, 1),
    name = "Cosine") +
  geom_tile() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 5),
    axis.text.y = element_text(size = 5)) +
  xlab("") + 
  ylab("")


# Jaccard
#season.feat2 <- textstat_frequency(season.dfm_lemma) %>%
  #filter(rank <= 50) 
#season.feat$feature

#season.jac <- textstat_simil(
  #season.dfm_lemma[, season.feat$feature],
  #method = "jaccard",
  #margin = "feature")

#season.jac.mat <- melt(as.matrix(season.euc)) # Convert the object to matrix then to data frame 

#ggplot(data = season.jac.mat, aes(x=Var1, y=Var2, fill=value)) +
  #scale_fill_gradient2(
    #low = "blue",
    #high = "red",
    #mid = "white",
    #midpoint = 0.5,
    #limit = c(0, 1),
    #name = "jaccard") +
  #geom_tile() + 
  #theme(
    #axis.text.x = element_text(angle = 45, hjust = 1, size = 5),
    #axis.text.y = element_text(size = 5)) +
  #xlab("") + 
  #ylab("")
  
# Cosine
#season.feat <- textstat_frequency(season.tf) %>%
  #filter(rank <= 40) 
#season.feat$feature

#season.cos <- textstat_simil(
  #season.tf[, season.feat$feature],
  #method = "cosine",
  #margin = "feature")
#season.cos.mat <- melt(as.matrix(season.cos)) # Convert the object to matrix then to data frame 

#ggplot(data = season.cos.mat, aes(x=Var1, y=Var2, fill=value)) +
  #scale_fill_gradient2(
    #low = "blue",
    #high = "red",
    #mid = "white",
    #midpoint = 0.5,
    #limit = c(0, 1),
    #name = "Cosine") +
  #geom_tile() + 
  #theme(
    #axis.text.x = element_text(angle = 45, hjust = 1, size = 5),
    #axis.text.y = element_text(size = 5)) +
  #xlab("") + 
  #ylab("")
```

## Clustering words
```{r echo=FALSE}
season.hcw <- hclust(as.dist(1 - season.cos))
plot(season.hcw)
```


# Term-Topic Analysis
```{r echo=FALSE}
season.tf <- dfm(season.tk_lemma)
season.lsa <- textmodel_lsa(x = season.tf, nd = 10) 
head(season.lsa$docs)
```

```{r echo=FALSE}
head(season.lsa$features)
```

```{r echo=FALSE, include=FALSE}
season.freq_lemma <- ntoken(season.tk_lemma)  
data.frame(season.freq_lemma,
           dim1 = season.lsa$docs[, 1]) %>% 
  ggplot(aes(season.freq_lemma, dim1)) + 
  geom_point() + 
  xlab("Number of tokens") + 
  ylab("LSA dim. 1")
```
We see that Dimension 1 is negatively correlated with the document length.

```{r echo=FALSE, include=FALSE}
n.terms <- 5
## For Dimension 2
w.order <- sort(season.lsa$features[, 2], decreasing = TRUE)
w.top2 <- c(w.order[1:n.terms], rev(rev(w.order)[1:n.terms]))
## For Dimension 3
w.order <- sort(season.lsa$features[,3], decreasing = TRUE)
w.top3 <- c(w.order[1:n.terms], rev(rev(w.order)[1:n.terms]))

# Topic 2
w.top2
```
Topic 2 is associated positively to "baby", "feel" and "love" and negatively with "ring", "night" and "mother".

```{r echo=FALSE, include=FALSE}
# Topic 3
w.top3
```
Topic 3 is associated positively to "time", "gablehouser" and "enter" and negatively with "ring", "past" and "feel".

```{r echo=FALSE}
biplot(
  y = season.lsa$docs[, 2:3],
  x = season.lsa$features[, 2:3],
  col = c("black", "red"),
  cex = c(0.3, 0.3),
  xlab = "Dim 2",
  ylab = "Dim 3")
```

```{r echo=FALSE}
w.subset <- 
  season.lsa$features[
    c(unique(c(names(w.top2), names(w.top3)))), 2:3]
biplot(
  y = season.lsa$docs[, 2:3],
  x = w.subset,
  col = c("black","red"),
  cex = c(0.5, 0.5),
  xlab = "Dim 2",
  ylab = "Dim 3")
```

## LDA using quanteda
```{r echo=FALSE}
set.seed(1234) #To create reproducible results
season.lda <- textmodel_lda(x = season.tf, k = 5)
seededlda::terms(season.lda, 5)
```

```{r echo=FALSE}
seededlda::topics(season.lda)
```

```{r echo=FALSE, include=FALSE}
seededlda::topics(season.lda) %>% table()
```

```{r echo=FALSE}
phi.long <- melt(
  season.lda$phi,
  varnames = c("Topic", "Term"),
  value.name = "Phi") 

phi.long %>% 
  group_by(Topic) %>% 
  top_n(5, Phi) %>% 
  ggplot(aes(reorder_within(Term, Phi, Topic), Phi)) + 
  geom_col(show.legend = FALSE) +
  coord_flip() +
  facet_wrap(~ Topic, scales = "free_y") +
  scale_x_reordered() + 
  xlab("Term") + 
  theme(
    axis.text.y = element_text(size = 5),
    strip.text = element_text(size = 5))
```


## Topic-Document Analysis
```{r echo=FALSE}
set.seed(1234)
theta.long <- melt(
  season.lda$theta,
  varnames = c("Doc", "Topic"),
  value.name = "Theta")

theta.long %>% 
  group_by(Topic) %>% 
  top_n(10, Theta) %>% 
  ggplot(aes(reorder_within(Doc, Theta, Topic), Theta)) + 
  geom_col(show.legend = FALSE) +
  coord_flip()+
  facet_wrap(~ Topic, scales = "free_y") +
  scale_x_reordered() + 
  xlab("Document") + 
  theme(
    axis.text.y = element_text(size = 5),
    strip.text = element_text(size = 5))
```

```{r echo=FALSE}
## 10 longest documents
## ntoken compute the lengths. They are sorted in decreasing order. 
n.doc <- 10
doc.list <- names(
  sort(ntoken(season.tk_lemma), decreasing = TRUE)[1:n.doc])
doc.list


theta.long %>% 
  filter(Doc %in% doc.list) %>%  
  ggplot(aes(reorder_within(Topic, Theta, Doc), Theta)) + 
  geom_col(show.legend = FALSE) +
  coord_flip()+
  facet_wrap(~ Doc, scales = "free_y") +
  scale_x_reordered() + 
  xlab("Document") +
   theme(
    axis.text.y = element_text(size = 5),
    strip.text = element_text(size = 5))
```


